\documentclass[11pt,a4paper]{moderncv}

% moderncv themes
\moderncvtheme[green]{classic}                 % optional argument are 'blue' (default), 'orange', 'red', 'green', 'grey' and 'roman' (for roman fonts, instead of sans serif fonts)
%\moderncvtheme[green]{classic}                % idem

% character encoding
\usepackage[utf8]{inputenc}                   % replace by the encoding you are using

% adjust the page margins
\usepackage[scale=0.76]{geometry}
\setlength{\hintscolumnwidth}{3cm}						% if you want to change the width of the column with the dates
%\AtBeginDocument{\setlength{\maketitlenamewidth}{6cm}}  % only for the classic theme, if you want to change the width of your name placeholder (to leave more space for your address details
%\AtBeginDocument{\recomputelengths}                     % required when changes are made to page layout lengths

% personal data
\firstname{Ing. Ján}
\familyname{Valiska}
\title{Curriculum vitae}               % optional, remove the line if not wanted
\address{Vrbnica 49}{07216}    % optional, remove the line if not wanted
\mobile{+421--949--749--124}                    % optional, remove the line if not wanted
%\phone{phone (optional)}                      % optional, remove the line if not wanted
%\fax{fax (optional)}                          % optional, remove the line if not wanted
%\email{jan.valiska@gmail.com}                      % optional, remove the line if not wanted
\email{jan.valiska@gmail.com}
%\homepage{homepage (optional)}                % optional, remove the line if not wanted
%\extrainfo{additional information (optional)} % optional, remove the line if not wanted
%\photo[64pt]{picture}                         % '64pt' is the height the picture must be resized to and 'picture' is the name of the picture file; optional, remove the line if not wanted
%\quote{Some quote (optional)}                 % optional, remove the line if not wanted

% to show numerical labels in the bibliography; only useful if you make citations in your resume
%\makeatletter
%\makeatother

% bibliography with mutiple entries
%\usepackage{multibib}
%\newcites{book,misc}{{Books},{Others}}

%\nopagenumbers{}                             % uncomment to suppress automatic page numbering for CVs longer than one page
%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\maketitle

\section{Education}
\cventry{2011--presence}{University}{Faculty of electrotechnics and informatics}{TUKE}{\textit{3rd degree}}{Telecommunication}  % arguments 3 to 6 can be left empty
\cventry{2009--2011}{University}{Faculty of electrotechnics and informatics}{TUKE}{\textit{2nd degree}}{Multimedia telecommunication}  % arguments 3 to 6 can be left empty
\cventry{2005--2009}{University}{Faculty of electrotechnics and informatics}{TUKE}{\textit{1st degree}}{Telecommunication}  % arguments 3 to 6 can be left empty
\cventry{2001--2005}{High school}{SPŠE}{\textit{Telecommunication technics}}{Michalovce}{}

\section{Doctoral thesis}
\cvline{Title}{\emph{Object tracking in video-sequences using Bayesian filters}}
\cvline{Supervisor}{prof. Ing. Stanislav Marchevský, CSc.}
\cvline{Description}{The work is focused on developing and testing of particle filters performance using various devices. Objects are represented using single color or color histograms.}

\section{Work experiences}
\cventry{2012--2015}{T-Systems s.r.o}{ICT Administrator}{Košice}{}{}{}

\section{Projects experiences}
\cventry{2013--presence}{UWB-SeNet}{Short-Range UWB Sensor Networks for Detection, Localization and Tracking of Moving Persons}{\textit{Software developing and testing of UWB radar system on 32-bit ARM architecture microprocessor boards}}{TUKE Košice}{}{}
\cventry{2013--presence}{PerLoc-3D-UWB}{Persons Localization in 3D Under Emergency Event based on UWB Radar System}{TUKE Košice}{}{}
\cventry{2011--2012}{CE II}{Center of Information and Communication Technologies for Knowledge Systems}{ITMS 26220120030}{TUKE Košice}{}{}

\section{Teaching experiences}
\cventry{2013}{SPŠE}{Two months experience in \textit{Informatics} course}{Arduino programming in C/C++ language}{Košice}{}{}
\cventry{2012--2014}{T-Systems s.r.o}{Internal Linux/Bash programming trainer}{Košice}{}{}

\section{Languages}
\cvline{Engish}{writing form--advanced, speaking--intermediate}

\section{Computer skills}
\cvcomputer{Operating systems}{GNU Linux, MS Windows, Dos, FreeBSD}{Typography}{\LaTeX, MS Office, OpenOffice\\LibreOffice}
\cvcomputer{Programming}{Bash/Zsh, C/C++, Python, Qt, Matlab, Ruby}{Web}{PHP, HTML, Nette Framework, Rails, jQuery, MySQL}
\cvline{OS Linux}{10 years of experiences in \textit{Linux} operating systems.}
\cvline{Web developing}{Creation of modern web applications using technologies like \textit{PHP Nette} and \textit{Ruby on Rails}.}
\cvline{Scripting}{Operating system automation using Bash/Python scripts}

\section{Skills in electronics}
    \cvline{Embedded devices}{Developing of simple systems using Arduino or other 8-bit AVR based or 32-bit ARM devices. Realised projects: Church 3-digit numeric display(IR controlled), Rotating coder controlled timer with 2x16 character LCD display, IR controlled HIFI DAC using Raspberry Pi ARM board.}
    \cvline{PCB}{Design and realisation of printed circuit boards using KiCAD software. Developing of PCB using negative photo-resist method}
    \cvline{Simulations}{Experience in electronic circuits simulation using ngspice}

\section{Competences and certificates}
\cvlistitem[-]{Driving license, types: B1, B, AM}
\cvlistitem[-]{Cisco Certified Network Assocciate(1-4.semester)}
\cvlistitem[-]{T-Systems internal security certifications}

\section{Interests}
\cvline{Open-source software}{I like open-source software because of possibility of changing and tweaking the source code.}
\cvline{Free time}{Family, literature, meaningful movie and soft-rock songs.}

\section{Personal informations}
\cvline{Date of birth}{\textit{14.10.1986} in Michalovce}
\cvline{Family state}{married}

%\nocite{*}

\end{document}
